---
title: "Analysing College Admissions from SAT scores"
author: "Syed Faaris Razi"
date: '2022-08-02'
geometry: "top=2cm,bottom=2cm"
output: pdf_document
---
In a Data Science Program from 2019 ($\underrightarrow{\textrm{link to}}$ [**\textcolor{purple}{Course and my Certificate of completion}**](https://udemy.com/certificate/UC-EMQU808M)), we were given various datasets to analyse and bring insights from, where one such data was on **College Admissions based on SAT scores** of students. 

Using *Python*, we applied Logistic Regression on said data to find the probability of Admittance from SAT scores. Here we shall implement the same analysis using *R*.

### The Data
```{r eval=TRUE, message=F, results = 'asis', warning = F}
library(tidyverse)
library(knitr, quietly = T)

admittance.raw = read.csv("2.01.+Admittance.csv") # Loading the data

# Map "No"/"Yes" values to an indicator column (Group) as 0's and 1's
admittance.SAT = admittance.raw %>% mutate(Group = Admitted) %>%
            mutate(Group = replace(Group, Group == "No", 0)) %>%
            mutate(Group = replace(Group, Group == "Yes", 1)) %>%
            mutate(Group = as.numeric(Group))

# Display both our raw and modified dataframes
df1 = kable(head(admittance.raw), format = 'latex')
df2 = kable(head(admittance.SAT), format = 'latex')

cat(sprintf("Preview of our CSV data (of %g rows):", nrow(admittance.raw)),
    c("\\begin{table}[h] \\centering ", df1, "\\hspace{1cm} \\centering ", df2,
    "\\caption{Raw dataframe (left),  New dataframe (right)} \\end{table}")) 
```

From the above, our raw data contains a numerical *SAT* column and a textual *Admitted* column of binary "No" and "Yes" responses. We modified this dataset to have a *Group* column of "No"/"Yes" values translated as numeric 0's and 1's (approriate format for Logistic Regression).

### Statistical summary of our Logisitic Regression:
```{r}
# glm()'s family = "binomial", since our dependant variable is binary (0's and 1's).
admittance.SAT.logit = glm(Group ~ SAT, data = admittance.SAT, family = binomial)
logreg_summary = summary(admittance.SAT.logit); logreg_summary
```

### Visualizing the Logisitic Regression
```{r message=F, warning=F}
b0 = logreg_summary$coefficients[1,1] # Getting the coefficients to
b1 = logreg_summary$coefficients[2,1] # be used inside our ggplot

# Setting annotations for our Plot
text_1 = bquote(atop(italic(b[0]) == .(b0), italic(b[1]) == .(b1)))
text_2 = bquote(atop(
                    italic(log)(hat(odds)) == ~~.(b0) ~ + ~ .(b1)*X,
                    where ~~ hat(odds):~~ e^{.(b0) ~ + ~ .(b1)*X}))
text_3 = bquote(and ~~ P(hat(Admitted)): ~~ hat(pi) == frac(hat(odds),1+hat(odds)))
x_text = mean(admittance.SAT$SAT)*(1 + 1/9) # key x-position for the labels

# Plotting the Logistic Regression with fitted values 
ggplot(admittance.SAT, aes(x = SAT, y = Group)) +
  geom_point(shape=1, position = position_jitter(width = .02, height = .02)) +
  stat_smooth(method = "glm", method.args = list(family = "binomial"), se = FALSE) +
  labs(y = "P(Admitted)") +
  annotate("text", x = x_text, y = 0.7, label = text_1, cex = 4.5, col = "#7070fa") +
  annotate("text", x = x_text, y = 0.45, label = text_2, cex = 4.2, col = "#2424f2") +
  annotate("text", x = x_text, y = 0.15, label = text_3, cex = 4.2, col = "#0404b8")
```