---
title: "Closing Prices for S&P 500, Microsoft, Apple, Facebook, and IBM"
author: "Syed Faaris Razi"
date: '2022-08-04'
geometry: "left=2.5cm,right=2.5cm,top=2cm,bottom=2cm"
output: html_document
always_allow_html: true
---

```{r echo=F, eval=TRUE, message=F, warning=F}
# Uncomment below code to install these necessary packages if they aren't already
# packages = c('rugarch','tseries','scales','fGarch','car','readxl','PEIP','plotly','MASS','tidyverse','PerformanceAnalytics','zoo','gridExtra','xtable','stats','quantmod','dygraphs','moments')
# 
# for (pkg in packages){
#   
#   # If we don't have some/one of the above packages, install them:
#   if(!(pkg %in% rownames(installed.packages()))){
#     install.packages(pkg, repos = "http://cran.us.r-project.org")
#     library(pkg, character.only = T)
#   }
# }

packages = c('PEIP', 'quantmod', 'car', 'PerformanceAnalytics', 'zoo', 'scales','fGarch', 'plotly', 'rugarch', 'MASS', 'moments', 'stats', 'tseries')

for (pkg in packages){
  library(pkg, character.only = T)
}
```

We will analyse a time-series dataset from *Yahoo Finance* on adjusted daily closing prices (from January $3^{rd}$ 2001
to June $8^{th}$ 2017) for S&P500 (^GSPC), IBM (IBM), Microsoft (MSFT), and Apple (AAPL).

### The Data

```{r  out.width='87%', fig.align = "center", results = 'hide'}

# The start and End dates od the downloadable data
dt.start = '2014-01-01'
dt.end = '2017-06-08'

# Getting the closing price data per company
companies = list(SP500=F, AAPL=T, MSFT=T, AAPL=T, FB=T, IBM=T)

for (company in names(companies)){ 
    instrument = company
    
    if (!companies[[company]]){
        instrument = '^GSPC' 
    }
    assign(company,
           get.hist.quote(instrument = instrument,
                          start = dt.start, end = dt.end, 
                          quote = c('AdjClose'),
                          retclass = 'zoo')
           )
}

data = merge(SP500, MSFT, AAPL, FB, IBM)
```

### Bollinger Band Forecasts for Microsoft

Lets visualize a Bollinger Bands plot using Simple Moving Average for the adjusted closing prices for the above companies (S&P 500, Microsoft ... ). The function below *bollinger.bands_plot* will produce interactive plots for the companies:

```{r warning=F, message=F}
library(dygraphs)

bollinger.bands_plot = function(company, n, name='company-XYZ'){

    Price = company$Adjusted
    
    sma = SMA(Price, n)
    sma.sd = rollapply(Price, width = n, FUN = sd)
    bolband.sd = sma + 2*sma.sd*c(-1,1)
    
    sma.m = sma[c(1:n-1)]
    
    bolband.lower = bolband.sd[1]
    bolband.upper = bolband.sd[2]
    
    
    sma.fore = cbind(Price, sma.m, bolband.lower, bolband.upper)
    
    dygraph(sma.fore, main = paste0('Bollinger Band Forecasts for ',name)) %>%
      dySeries('Price', label = 'Price', col = 'black') %>%
      dySeries('sma.m', label = 'SMA', col = 'red') %>%
      dySeries('bolband.lower', label = 'LB', col = 'green') %>%
      dySeries('bolband.upper', label = 'UB', col = 'blue') %>%
      dyLegend(width=300) %>%
      dyRangeSelector(height = 20)
}
```

```{r message=F, warning=F}
all_companies = list('S&P 500'=SP500, Microsoft=MSFT, Apple=AAPL, Facebook=FB, 'IBM'=IBM)

n = 30

# Plotting per company
bollinger.bands_plot(SP500, n = n, name = 'S&P 500')
bollinger.bands_plot(SP500, n = n, name = 'Microsoft')
bollinger.bands_plot(SP500, n = n, name = 'Apple')
bollinger.bands_plot(SP500, n = n, name = 'Facebook')
bollinger.bands_plot(SP500, n = n, name = 'IBM')
```